Prestige as a Driving Force in Cultural Transmission

### 2022-04-04 ms/PrestigeBias.tex
update

\begin{proof}
The initial prestige of role-model $j$ based on \cref{eq:prestige} is
\begin{equation}\label{eq:initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
\end{equation}
The denominator of \cref{eq:initial_prob} can also be formulated as:
\begin{equation}\label{eq:denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
Using \cref{eq:denominator} we get, % TODO something is missing here? how did you get E[KNj] to relate to the previous two equations?
\begin{equation}
\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
completing the proof.
\end{proof}

@@

\paragraph{Numerical validation.}
To be added
% TODO what about a numerical validation for GBD?

@@

For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required. % TODO did you test other distributions?
% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{
  \textbf{Number of simulations needed to get a good approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. % 1000 simulations of the model or of DM ??
  Markers for average value across simulations, error bars for 95\% confidence interval.
  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
  % TODO
  % remove legend
  % change y labels: "Fixation probability" "Fixation time"
  % change x label: "Number of simulations"
  % Kimura - black solid line
  % I removed J as you give beta(A) below, ok
  % it is not clear what "number of simulations needed" means.
  % what does "good enough" mean?
  % maybe y axis should be in relative error?
  % you should point to the equation for kimura.
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{proof}
The initial prestige of role-model $j$ based on \cref{eq:prestige} is
\begin{equation}\label{eq:initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
\end{equation}
The denominator of \cref{eq:initial_prob} can also be formulated as:
\begin{equation}\label{eq:denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
\begin{equation}
\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
completing the proof.
\end{proof}

@@

% TODO what about a numerical validation for GBD?
% ANS - The results of this approximation are contained in the next DM approximation. In here we find the expected number of copiers for a single role-model, and in the DM we find that (and get the same results of course) and more. I can make the Numerical Validation a subsection and say it's for both.

@@

For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required.
% TODO did you test other distributions?
% ANS - No, mainly because I didn't know what paremeters to choose, we should discuss

% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
% ANS - observed vs expected of what? Make a histogram of number of copiers per role-model? just the top role-models?

% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{
  \textbf{Number of simulations needed to get a good approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. 
  Markers for average value across simulations, error bars for 95\% confidence interval.
  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
  % TODO
  % Kimura - black solid line
  % I removed J as you give beta(A) below, ok
  % it is not clear what "number of simulations needed" means.
  % what does "good enough" mean?
  % maybe y axis should be in relative error?
  % you should point to the equation for kimura.
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
